Exploratory data analysis

### 2020-12-25 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

@@

```{r eda-3 }
plot_prcomp(vi_data_corrected_buffer2)
```

@@

```{r eda-5 }
intro <- introduce(nri_data_corrected_buffer2)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-6 }
plot_prcomp(nri_data_corrected_buffer2)
```

@@

```{r eda-8 }
intro <- introduce(bands_data_corrected_buffer2)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-10 }
plot_prcomp(bands_data_corrected_buffer2)
```

>>>>

VI = Vegetation Indices
NRI = Normalized Ratio Indices
HR = Hyperspectral reflectances (image bands)

@@

```{r eda-3 }
vi_data_corrected_buffer2_no_defol = vi_data_corrected_buffer2
vi_data_corrected_buffer2_no_defol$defoliation <- NULL
pca <- DataExplorer::plot_prcomp(vi_data_corrected_buffer2_no_defol,
  variance_cap = 0.98,
  ggtheme = ggpubr::theme_pubclean()
)
pca[[1]]
```

@@

```{r eda-5 }
# remove response
nri_data_corrected_buffer2$defoliation <- NULL

intro <- introduce(nri_data_corrected_buffer2)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-6 }
pca <- DataExplorer::plot_prcomp(nri_data_corrected_buffer2,
  variance_cap = 0.98,
  ggtheme = ggpubr::theme_pubclean()
)
pca[[1]]
```

@@

```{r eda-8 }
# remove response
bands_data_corrected_buffer2$defoliation <- NULL

intro <- introduce(bands_data_corrected_buffer2)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-10 pca-bands, dev = c("png", "pdf")}
pca <- DataExplorer::plot_prcomp(bands_data_corrected_buffer2,
  variance_cap = 0.98,
  ggtheme = ggpubr::theme_pubclean()
)
pca[[1]]
```
